Tropical Mathematics for the Lambda Calculus

### 2023-01-17 section4.tex
commit

Let us now consider the case of bounded exponentials $!_{\leq n}X$:
\begin{proposition}\label{prop:boundedlip}
If a tLs $f: \Lawv^{X}\to \Lawv^{Y}$ arises from a matrix $\check f:{\C M_{\leq n}(X)}\times Y\to \Lawv$, then $f$ is $n$-Lipschitz-continuous.
\end{proposition}
\begin{proof}[Proof sketch]
This follows from Proposition \ref{prop:troplinear} and the remark that, for all $x\in \Lawv^{X}$, $\| (!_{n} x)-(!_{n} y)\|_{\infty}\leq n\cdot \| x- y\|_{\infty}$, where $!_{n} x$ is the restriction of $! x$ to $\C M_{\leq n}(X)$.%
%Using the fact that $f(\B x)_{b}=\inf_{\mu\in \C M_{\leq n}(X)}\{ \check f_{\mu,b}+ \mu (!_{n}\B x) \}$, where $!_{n}\B x\in \Lawv^{\C M_{\leq n}(X)}$ is given by 
%$(!_{n}\B x)_{[a_{1},\dots, a_{k}]}=\sum_{i=1}^{k}\B x_{a_{i}}$, 
%it suffices to check that $\| (!_{n}\B x)-(!_{n}\B y)\|_{\infty}\leq n\cdot \| \B x-\B y\|_{\infty}$ and apply Proposition \ref{prop:troplinear}.
\end{proof}
This result is perfectly analogous to what happens in the metric models discussed in Section \ref{section2}, the bounded exponentials $!_{n}$ playing the role of the re-scaling trick.

>>>>

Let us now consider the case of bounded exponentials:
\begin{proposition}\label{prop:boundedlip}
If a tLs $f: \Lawv^{X}\to \Lawv^{Y}$ arises from a matrix $\check f:!_{n}X\times Y\to \Lawv$, then $f$ is $n$-Lipschitz-continuous.
\end{proposition}
\begin{proof}[Proof sketch]
This follows from Proposition \ref{prop:troplinear} and the remark that, for all $x\in \Lawv^{X}$, $\| (!_{n} x)-(!_{n} y)\|_{\infty}\leq n\cdot \| x- y\|_{\infty}$, where $!_{n} x$ is the restriction of $! x$ to $\C M_{\leq n}(X)$.%
%Using the fact that $f(\B x)_{b}=\inf_{\mu\in \C M_{\leq n}(X)}\{ \check f_{\mu,b}+ \mu (!_{n}\B x) \}$, where $!_{n}\B x\in \Lawv^{\C M_{\leq n}(X)}$ is given by 
%$(!_{n}\B x)_{[a_{1},\dots, a_{k}]}=\sum_{i=1}^{k}\B x_{a_{i}}$, 
%it suffices to check that $\| (!_{n}\B x)-(!_{n}\B y)\|_{\infty}\leq n\cdot \| \B x-\B y\|_{\infty}$ and apply Proposition \ref{prop:troplinear}.
\end{proof}
This result is perfectly analogous to what happens in the metric models discussed in Section \ref{section2}, the bounded exponentials $!_{n}$ playing the role of the re-scaling trick.
